\documentclass[]{article}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifxetex
  \usepackage{fontspec,xltxtra,xunicode}
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
\else
  \ifluatex
    \usepackage{fontspec}
    \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \else
    \usepackage[utf8]{inputenc}
  \fi
\fi
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex,
              colorlinks=true,
              linkcolor=blue]{hyperref}
\else
  \usepackage[unicode=true,
              colorlinks=true,
              linkcolor=blue]{hyperref}
\fi
\hypersetup{breaklinks=true, pdfborder={0 0 0}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\title{Final}
\author{2013-12-03}
\date{Eric Rasche}

\begin{document}
\maketitle

\section{Take Home}

I have no illusions as to how busy all of you are. However, in the event
that you wish to work on creating packages some more, I've written a
spec for a take home project. If you complete this, feel free to email
it to me and I'll check it over for you.

\section{Specification}

At least try to achieve the main objectives. If you are feeling brave
and have time for reading and coding, then feel free to attempt the
other objectives! They should require some reading and searching the web
for information. If you get stuck, email me and I will be happy to send
you pointers.

\subsection{Main objectives}

\begin{itemize}
\item
  Should provide a command that does something, anything. Recommendation
  of printing static text.
\item
  Control file should be properly filled out such that the package can
  install on a \emph{clean} system without issue.
\item
  Invokes update-alternatives to create and remove alternate names for
  itself.
\item
  Complete man page with all of the proper sections filled out so I can
  figure out what it does just by \texttt{man yourcommand}.
\item
  Sign your package
\end{itemize}
\subsection{Optional objectives}

These should be well within your reach.

\begin{itemize}
\item
  Scripting
  \begin{itemize}
  \item
    Ask the user questions about how the programme should be configured
    in \texttt{postinst} (hint,
    \href{http://www.fifi.org/doc/debconf-doc/tutorial.html}{read this})
  \item
    Clean up all possibly created files in \texttt{postrm}
  \end{itemize}
\end{itemize}
\subsection{Advanced Objectives}

Feel free to IM/email me on these, I am not 100\% familiar with the
\texttt{dbconfig} package and will be happy to offer any assistance I
can.

\begin{itemize}
\item
  Daemon
  \begin{itemize}
  \item
    Should run as a daemon, install \texttt{/etc/init.d/} script
  \item
    Should start and stop the daemon in \texttt{postinst} and start
  \end{itemize}
\item
  Database
  \begin{itemize}
  \item
    Use \texttt{dbconfig-common}.
  \item
    Take advantage of \texttt{debian-sys-maint} for MySQL users.
  \end{itemize}
\end{itemize}

\end{document}
